Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
work on book table
more details in dep graph caption

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while straight-line boxes represent maintained Coq packages. Dark grey packages are maintained in the \Hydras GitHub repository, while light grey packages are maintained in other \community repositories.}
  \label{fig:genealogy}
\end{figure}

@@

>>>>

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while straight-line boxes represent maintained Coq packages. Dark grey packages are maintained in the \Hydras GitHub repository, while light grey packages are maintained in other \community repositories. Dotted lines represent Coq code ancestry, while regular lines represent direct code dependencies.}
  \label{fig:genealogy}
\end{figure}

@@

\begin{table}
  \centering
  \footnotesize
  \begin{tabular}{lll}
  \hline
  \textbf{Title} & \textbf{Year} & \textbf{Category}\\
  \hline
  Coq'Art~\cite{BC04} & 2004 & Traditional\\
  Formal Reasoning About Programs~\cite{Chlipala2017} & 2017 & Traditional\\
  Software Foundations~\cite{Pierce2007} & 2007 & Executable\\
  Program Logics for Certified Compilers~\cite{Appel2014} & 2014 & Traditional\\
  \end{tabular}
  \caption{Coq book comparison.}
  \label{tbl:loc}
\end{table}
